Case study validations of automatic bullet matching

### 2018-10-25 index.Rmd
Move text around a bit, phrasing

\svp{Examining land-to-land scores provides more details about the matching algorithm's performance. Figure \ref{fig:compare-land-to-land} shows density curves and rug plots for each study. There is some overlap between known matching and known non-matching land-to-land scores; in many cases the random forest scores for these overlapping values are more extreme than the corresponding ccf scores. This suggests that the matching algorithm is sensitive to the presence of LEAs which have low land-to-land match scores, such as the matches of bullets `I' and `F' in the Hamby 44 study. }

\svp{In \autoref{fig:rocs}, the Houston FSI G1 and G3 curves and the Phoenix PD curve show excellent performance; Houston FSI G2 and Hamby 44 show relatively good performance. Area under the curve (AUC) values, which summarize ROC curves, are shown in \autoref{tab:aucs}. AUC values are useful for differentiating between poor, good, and excellent model performance, but are not particularly useful when determining which of several models with approximately the same level of performance should be used \citep{marzban_roc_2004}. Hamby 44 is the only study with a somewhat noticable difference between the AUC score for RF compared to ccf, and even that difference is relatively small.}

@@

```{r compare-land-to-land, fig.width = 8, fig.height = 4, fig.cap="Density curves of land-to-land similarity scores from cross-correlation (top) and RF scores (bottom). Different colors indicate same source and phase versus different source or out-of-phase matches. The random forest scores tend to be more extreme than the cross correlation scores alone."}
all_lands %>% 
  gather(key = "measure", value = "value", ccf, rfscore) %>%
  mutate(measure = factor(measure, levels = c("ccf", "rfscore"),
                          labels = c("Cross-correlation", "RF score")),
         study = paste(study, group1) %>% str_trim() %>% factor(levels = c("Hamby 44", "Phoenix PD", "Houston FSI G1", "Houston FSI G2", "Houston FSI G3"))) %>%
  ggplot(aes(
    x = value, fill = sameland,
    colour = sameland
  )) +
  geom_density(alpha = 0.6) +
  geom_rug(alpha = 0.5/12, show.legend = F) +
  facet_grid(measure ~ study) +
  theme_bw() +
  scale_fill_manual("Same source & best sequence", values = c("darkgrey", "darkorange")) +
  scale_colour_manual("Same source & best sequence", values = c("darkgrey", "darkorange")) +
  scale_x_continuous("Land-to-Land scores", limits = c(0, 1)) +
  theme(legend.position = "bottom") +
  geom_hline(yintercept = 0, show.legend = F)
```
```{r rocs, fig.cap="ROC curves for all studies based on land-to-land comparisons \\svp{of the random forest score}.", fig.width = 4.5, fig.height = 3, out.width = ".5\\textwidth"}
library(plotROC)
library(pROC)
all_lands %>% 
  ggplot(aes(colour = interaction(study, group1, sep = " "))) +
  geom_roc(aes(m = rfscore, d = as.numeric(sameland)), 
           labels =FALSE, pointsize = 0, alpha = 0.8) +
  theme_bw() +
  xlab("Fraction False Positives") +
  ylab("Fraction True Positives") +
  scale_colour_manual("Study", values = c("#fe9929", "#aa0000",
                                         "#74a9cf", "#2b8cbe", "#045a8d"))
```

@@

>>>>

\svp{Examining land-to-land scores provides more details about the matching algorithm's performance. \autoref{fig:compare-land-to-land} shows density curves and rug plots for each study. There is some overlap between known matching and known non-matching land-to-land scores; in many cases the random forest scores for these overlapping values are more extreme than the corresponding ccf scores. This suggests that the matching algorithm is sensitive to the presence of LEAs which have low land-to-land match scores, such as the matches of bullets `I' and `F' in the Hamby 44 study. Comparing this to the bullet-to-bullet score density plot shown in \autoref{fig:compare}, we see that there is much greater separation between the same-source and different-source densities for each study in the bullet-to-bullet comparisons than in the land-to-land comparisons, that is, one or two poorly matching lands does not prevent the bullet from showing a matching score, though if there are only weak matches on a few lands, such as the marked Hamby 44 comparisons in \autoref{fig:compare}, the overall score may be affected. }

@@

```{r compare-land-to-land, fig.width = 8, fig.height = 4, fig.cap="Density curves of land-to-land similarity scores from cross-correlation (top) and RF scores (bottom). Different colors indicate same source and phase versus different source or out-of-phase matches. The random forest scores tend to be more extreme than the cross correlation scores alone."}
all_lands %>% 
  gather(key = "measure", value = "value", ccf, rfscore) %>%
  mutate(measure = factor(measure, levels = c("ccf", "rfscore"),
                          labels = c("Cross-correlation", "RF score")),
         study = paste(study, group1) %>% str_trim() %>% factor(levels = c("Hamby 44", "Phoenix PD", "Houston FSI G1", "Houston FSI G2", "Houston FSI G3"))) %>%
  ggplot(aes(
    x = value, fill = sameland,
    colour = sameland
  )) +
  geom_density(alpha = 0.6) +
  geom_rug(alpha = 0.5/12, show.legend = F) +
  facet_grid(measure ~ study) +
  theme_bw() +
  scale_fill_manual("Same source & best sequence", values = c("darkgrey", "darkorange")) +
  scale_colour_manual("Same source & best sequence", values = c("darkgrey", "darkorange")) +
  scale_x_continuous("Land-to-Land scores", limits = c(0, 1)) +
  theme(legend.position = "bottom") +
  geom_hline(yintercept = 0, show.legend = F)
```

```{r rocs, fig.cap="ROC curves for all studies based on land-to-land comparisons \\svp{of the random forest score}.", fig.width = 4.5, fig.height = 3, out.width = ".5\\textwidth"}
library(plotROC)
library(pROC)
all_lands %>% 
  ggplot(aes(colour = interaction(study, group1, sep = " "))) +
  geom_roc(aes(m = rfscore, d = as.numeric(sameland)), 
           labels =FALSE, pointsize = 0, alpha = 0.8) +
  theme_bw() +
  xlab("Fraction False Positives") +
  ylab("Fraction True Positives") +
  scale_colour_manual("Study", values = c("#fe9929", "#aa0000",
                                         "#74a9cf", "#2b8cbe", "#045a8d"))
```

@@

\svp{In \autoref{fig:rocs}, the Houston FSI G1 and G3 curves and the Phoenix PD curve show excellent performance; Houston FSI G2 and Hamby 44 show relatively good performance. Area under the curve (AUC) values, which summarize ROC curves, are shown in \autoref{tab:aucs}. AUC values are useful for differentiating between poor, good, and excellent model performance, but are not particularly useful when determining which of several models with approximately the same level of performance should be used \citep{marzban_roc_2004}. Hamby 44 and Phoenix PD are the only studies with a somewhat noticable difference between the AUC score for RF compared to ccf, and even those differences are relatively small: .03 and -.01, respectively.}
